---
title: "Preperation of Decision Data"
format:
  html:
    include: false
    self-contained: true
---

```{r setup, warning = FALSE, message = FALSE}
library(dplyr)
library(readr)
library(tidyr)
library(data.table)
library(vroom)
library(magrittr)
library(here)
library(ggplot2)
library(haven)
```

# Import data {.hidden .unnumbered .unlisted}
First, we obtain a list of files that we will import.
```{r}
# List files from Bilendi
bilendi_files <- list.files(path = here::here("1_Data", "1_raw", "2023_11_Bilendi"),
          pattern = "decision_block_",
          recursive = TRUE,
          full.names = TRUE)

# List files from Dynata
dynata_files <- list.files(path = here::here("1_Data", "1_raw", "2024_12_Dynata"),
          pattern = "decision_block_",
          recursive = TRUE,
          full.names = TRUE)

# Combine both lists into one
files <- c(bilendi_files, dynata_files)

# List files
files

# Import and bind all files
decision_tasks <- vroom::vroom(files, col_types = list(participant_label = col_character()))

# Filter for completes (some subjects in the data have dropped out)
complete_sl <- read_csv(here::here("1_Data", "1_raw", "2023_11_Bilendi", "Completes_sl12.csv"),
                        col_types = list(participant_label = col_character()))
complete_fl <- read_csv(here::here("1_Data", "1_raw", "2023_11_Bilendi", "Completes_fl.csv"),
                        col_types = list(participant_label = col_character()))
complete_fl2 <- read_csv(here::here("1_Data", "1_raw", "2024_12_Dynata", "Completes_fl2.csv"),
                        col_types = list(participant_label = col_character()))

# Rename "Indonesia" to "indonesia" in complete_sl, complete_fl, and decision tasks as these cause issues in further, case sensitive analyses
complete_sl$session_label <- tolower(complete_sl$session_label)
complete_fl$session_label <- tolower(complete_fl$session_label)
decision_tasks$session_label <- tolower(decision_tasks$session_label)

write_csv(complete_sl, file = here::here("1_Data", "1_raw", "2023_11_Bilendi", "Completes_sl12.csv"))
write_csv(complete_fl, file = here::here("1_Data", "1_raw", "2023_11_Bilendi", "Completes_fl.csv"))

completes <- rbind(complete_sl, complete_fl, complete_fl2)

decision_tasks %<>% inner_join(y = completes, by = c("participant_label", "session_label"))
```


# Data prep {.hidden .unnumbered .unlisted}
```{r}
# We add the variable "price of redistribution" to the raw data.
# We define pog = (to_goal_1_max / to_goal_2_max)
decision_tasks %<>% 
  mutate(price_of_redist = to_goal_1_max / to_goal_2_max)
```


Some column filtering and renaming.
```{r}
decision_tasks %<>%
  rename(to_goal1 = to_goal_1,
         to_goal2 = to_goal_2,
         to_goal1_max = to_goal_1_max,
         to_goal2_max = to_goal_2_max)

# The goal codes are only recorded in the first round, so we fill the following rows from the previous one
decision_tasks %<>%
  fill(goal1_code, goal2_code,
       .direction = "down")

# Add a variable for the goal pair
decision_tasks %<>%
  mutate(goal_pair = paste0(goal1_code, "-", goal2_code),
         .after = goal2_code)

# Sort by session name and subject id
decision_tasks %<>% arrange(session_label, participant_label)

# We introduce a block_number variable that informs about the task block (= number of the goal pair from 1 - 5)
block_numbers <- decision_tasks %>%
  group_by(participant_label, goal_pair) %>%
  tally() %>%
  mutate(block_number = row_number()) %>% 
  select(-n)

decision_tasks %<>% left_join(y = block_numbers, by = c("participant_label", "goal_pair"))
```


For the Matlab estimation, we also need the _share_ of budget given to goal 1 [goal 2]. So we will calculate them here.
```{r}
decision_tasks %<>%
  mutate(price_goal1 = 1 / to_goal1_max,
         price_goal2 = 1 / to_goal2_max,
         price_ratio = price_goal1 / price_goal2, # This is the inverse of the price of redistribution!
         to_goal1_p = to_goal1 * price_goal1 / (to_goal1_max * price_goal1), # Divide by the budget
         to_goal2_p = to_goal2 * price_goal2 / (to_goal2_max * price_goal2))
```


Note, we will introduce a new unique subject id because the current `session_subject_id` is only unique within a session.
```{r}
decision_tasks %<>%
  group_by(participant_label) %>%
  mutate(id = cur_group_id(), .before = participant_label)
```


# Export {.hidden .unnumbered .unlisted}
```{r}
# Save table
write_csv(decision_tasks,
          file = here::here("1_Data", "2_processed", "Data_decision_task_online.csv"))
```

